fig4

### 2020-03-02 analysis/figure-4.Rmd
new fig 4

```{r fig4, fig.height=7, fig.width=7}
geneids <- read_csv("../metadata/00_geneinfo.csv")

@@

hypgenes <- read_csv("../results/DEseq2/female_hypothalamus_hatch_n5_DEGs.csv") %>%
  arrange(desc(logpadj)) %>% head(., n = 2) %>% pull(gene)
hypgenes

pitgenes <- read_csv("../results/DEseq2/female_pituitary_inc.d9_inc.d17_DEGs.csv") %>%
  arrange(desc(logpadj)) %>% head(., n = 2) %>% pull(gene)
pitgenes

gongenes <- read_csv("../results/DEseq2/female_gonad_lay_inc.d3_DEGs.csv") %>%
  arrange(desc(logpadj)) %>% head(., n = 2) %>% pull(gene)
gongenes

@@

plottopgenes <- function(whichgenes, whichtissue, whichsex, mysubtitle, whichtstages){
  candidates  <- allvsd %>%
    filter(gene %in% whichgenes) %>%
    dplyr::mutate(sextissue = sapply(strsplit(file_name, '_vsd.csv'), "[", 1)) %>%
    dplyr::mutate(sextissue = sapply(strsplit(sextissue, '../results/DEseq2/'), "[", 2)) %>%
    dplyr::mutate(sex = sapply(strsplit(sextissue, '\\_'), "[", 1),
                tissue = sapply(strsplit(sextissue, '\\_'), "[", 2),
                treatment = sapply(strsplit(samples, '\\_'), "[", 4)) %>%
    dplyr::mutate(treatment = sapply(strsplit(treatment, '.NYNO'), "[", 1)) %>%
    dplyr::select(sex, tissue, treatment, gene, samples, counts) %>%
    filter(tissue == whichtissue, sex %in% whichsex)

@@

a <- plottopgenes(hypgenes, "hypothalamus", c("female"), "hypothalamus", c("hatch", "n5")) 
b <- plottopgenes(pitgenes, "pituitary", c("female"), "pituitary", c("inc.d9", "inc.d17")) 
c <- plottopgenes(gongenes, "gonad", c("female"), "gonads", c("lay", "inc.d3"))

>>>>

```{r data}
geneids <- read_csv("../metadata/00_geneinfo.csv")

@@

hypgenes <- c("POMC", "DRD1")
pitgenes <- c("PRL", "BRCA1")
gongenes <- c("AVPR1A", "PRLR")

@@

```

```{r fig4, fig.height=7, fig.width=7}
plottopgenes <- function(whichgenes, whichtissue, whichsex, mysubtitle, whichtstages){
  candidates  <- allvsd %>%
    filter(gene %in% whichgenes) %>%
    dplyr::mutate(sextissue = sapply(strsplit(file_name, '_vsd.csv'), "[", 1)) %>%
    dplyr::mutate(sextissue = sapply(strsplit(sextissue, '../results/DEseq2/'), "[", 2)) %>%
    dplyr::mutate(sex = sapply(strsplit(sextissue, '\\_'), "[", 1),
                tissue = sapply(strsplit(sextissue, '\\_'), "[", 2),
                treatment = sapply(strsplit(samples, '\\_'), "[", 4)) %>%
    dplyr::mutate(treatment = sapply(strsplit(treatment, '.NYNO'), "[", 1)) %>%
    dplyr::select(sex, tissue, treatment, gene, samples, counts) %>%
    filter(tissue == whichtissue, sex %in% whichsex)

@@

a <- plottopgenes(hypgenes, "hypothalamus", c("female"), "hypothalamus", c("hatch", "n5")) 
b <- plottopgenes(pitgenes, "pituitary", c("female"), "pituitary", c("inc.d9", "inc.d17")) 
c <- plottopgenes(gongenes, "gonad", c("female"), "gonads", c("lay", "inc.d3")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
